%-------------------------
% Resume in Latex
% Author : Andrei Tuta
% License : MIT
%------------------------

\documentclass[12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}\usepackage{hyphenat}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{datetime}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

{\small\begin{tabular}[c]{l}
  \textbf{Manchester,UK}\\
  \href{http://www.github.com/andreituta}{github.com/andreituta}\\
  \href{http://www.linkedin.com/in/andreituta}{linkedin.com/in/andreituta}
\end{tabular}}\hfill%
{\Large\bfseries\begin{tabular}[c]{c}
  Andrei Nicolae Tuță
\end{tabular}}\hfill%
{\small\begin{tabular}[c]{r}
  07859730064  \\
  \href{mailto:tuta.andrei96@gmail.com}{andrei.tuta@atdev.uk}
  \\ 
  \monthname, 2021
    
    
\end{tabular}}%


%-----------CAREER-----------------
\section{Professional Profile}
        
          { \quad \quad  Versatile professional with development experience ranging in size from small private projects to full-scale applications. Currently working on developing an online and mobile e-commerce product's functionality and CRM, entrusted worldwide by customers.       
          
            \quad \quad  Always interested in learning more about emerging OSS technologies and make new professional connections.
          }

%-----------EXPERIENCE-----------------
\section{Professional History}
  \resumeSubHeadingListStart
  
  \resumeSubheading
    {Aeroparker}{Stockport, UK}
    {Java Developer}{Oct 2018 - Jul 2021}
      \resumeItemListStart
        \resumeItem{Team leader}
            {
            Managed a team of 4 developers through daily stand ups, code reviews and pair programming.
            \newline
            Actively involved in estimation sessions and software development planning process.
            }
       
        \resumeItem{BI tool}
            { Developed a BI tool used daily by a large number of clients to get product metrics through API calls and using D3.js for visualisation (later improved to use AWS QuickSight). }
            
        \resumeItem{Java}{
            Planned, designed and implemented new features for the Java core project, built using Apache Tomcat, AJAX and JSP.
            \newline
            Developed implementations of Spring based microservice applications using JOOQ, JWT, SQS and Thymeleaf. 
            }
          
      \resumeItemListEnd
      
%   \resumeSubheading
%     {URJ 6 Points Sci-tech}{Byfield, MA}
%     {Counselor/ Specialist}{Jun - Aug 2018}
%       \resumeItemListStart
%         \resumeItem{Programming assistant}
%           {Helped instructors deliver the programming workshop, focused on teaching elementary Java, and Processing}
%         \resumeItem{Workshop Instructor}
%           {Volunteered to run my own workshop, teaching participants basic HTML, CSS, JS for coding a virtual board game.}
%       \resumeItemListEnd
    
    \resumeSubheading
    {Birmingham City University}{Birmingham, UK}
    {Technical Student Assistant}{Sep 2017 - Jun 2018}
      \resumeItemListStart
        \resumeItem{Student Assistant}
          {Managed and aided groups of students during courses and activities. Tasks varied explaining programming concepts and active development to }
        \resumeItem{Student Ambassador}
            { Organised large scale events and provided tech support and resources. }
        \resumeItem{Innovation Fest Mentor}
          {Supervised two teams of students with the planning, technical development and pitching of their entries for a local technology contest, which they won. }
      \resumeItemListEnd

    \resumeSubheading
    {Oracle Romania}{Bucharest, RO}
    {Database Administrator}{Jun - Sep 2017}
      \resumeItemListStart
        \resumeItem{Oracle DBA training}
          {Received training covering topics such as administration, back-up, recovery and automation. 
          \newline
          Participated in guided boot camps on MySQL and Orace SQL}
      \resumeItemListEnd
      
    
    % \resumeSubheading
    % {The Business Information Portal}{Birmingham,UK}{Software Developer}{Oct 2015 - Sep 2016}
    %     \resumeItemListStart
    %         \resumeItem
    %           {Part-time development}
    %           {Worked within a small team to develop solutions for people with visual impairment. Gained experience working within a large code base and improved at writing clean, testable  code.}
    %          \resumeItem
    %          {Testing}
    %          {Applied Agile methodologies and CI processes with Test Driven software development in various environments.Learned the importance of risk management in software: continuous builds, Quality Assurance and release cycles .}
    %     \resumeItemListEnd
      
      \resumeSubheading
    {Logika IT Solutions}{Bucharest, RO}
    {Junior Database Administrator }{Jun - Aug 2016}
      \resumeItemListStart
        \resumeItem{Summer internship}
        {Worked as a trainee in a team of 4 people managing databases for multiple local clients. Other responsibilities included writing reports and suggestions on ways to improve the work-flow and diminish cost. }
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \item{
     {\textbf{Programming Languages}}{:  Java, Javascript, SQL, Python}}
     \item{
     {\textbf{Technologies}}{: AWS(EC2, S3, SQS), Springboot, Tomcat 7\&9, node-modules, MySQL, Testing (JUnit Jupiter, Mockito, Selenium), Flask, Jinja, Docker, Git}
    }
    \item{
    {\textbf{Language proficiency}}{: Romanian, English, French, Spanish}    
    }
 \resumeSubHeadingListEnd
 

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
  {Birmingham City University}{Birmingham, UK}
  {Data Analysis, Software Engineering 
  \& Database administration}
  {2015 - 2018}
    \resumeSubheading
  {Universidad de Alcala}{Alcala de Henares, SP}
  {Software Design, Cloud computing \& Agile Development }
  {Jan - Jun 2017}
  \resumeSubHeadingListEnd



% % ------------Extracurricular activities------------
 \section{Extracurricular activities}
    \resumeSubHeadingListStart
         \resumeSubheading
        {Participant} {CodeUp Stockport}
        {Participating and helping our members at our monthly Meetups.}{Jul 2019 - Mar 2020}
        \resumeSubheading
        {Writer}{Medium}
        {Writing articles featuring subjects related to programming \& literature.}
        {2017 - present}
          \resumeSubheading
        {Camp counselor}{URJ 6Points Sci tech}
        {Assisted \& organised programming workshops for campers on Java \& Processing}
        {Jun - Aug 2018}
        % \resumeSubheading
        % {Outward Mobility Ambassador} {BCU CEBE}
        % {Managing \& recruiting students for international programs \& social media development.} {Jan - Jun 2018}
         \resumeSubheading
        {Society Advisor}
        {HaCS}
        {Helped planning, managing and volunteering for hosting local Hackathons.}
        {2015 - 2018}
        \resumeSubheading
        {President}
        {BCU RoSoc}
        {Event planning, budgeting \& team management.}{2016 - 2018}
        \resumeSubheading
        {Secretary}
        {Rotaract Club Birmingham}
        {PR \& note-taking.}{2015 - 2017}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
